---
title: "Cane Toad Invasion"
---

Cane toads are large, poisonous toads native to South America but which are spreading in [Australia](australia.html) and [Florida](florida.html).

**Background information**

* [What is a cane toad?](https://eol.org/pages/333309)
* [Invasive Species Impact Biodiversity from ActionBioScience](http://www.actionbioscience.org/biodiversity/simberloff.html)
* [Strange facts about cane toads from Mental Floss](http://mentalfloss.com/article/75879/10-bumpy-facts-about-cane-toads)

**Videos**

```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::include_url("https://www.youtube.com/embed/rI8IiLqIEV0", height = "400px")
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::include_url("https://player.vimeo.com/video/49886782?title=0&byline=0&portrait=0", height="400px")
```

**Investigation**

Using [One Zoom](https://www.onezoom.org/life/@Rhinella_schneideri=120195#x658,y210,w0.2677), what are the Cane Toad’s closest relatives? Are other relative of the cane toad also invasive species?  Why do you think that? 
